A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-10 main.tex
Fix the defnition of Context.
Polish.

  We study a dependently typed extension of a multi-stage programming
  language \`a la MetaOCaml, which supports quasi-quotation and
  cross-stage persistence for manipulation of code fragments as
  first-class values and run for execution of programs dynamically
  generated by the code manipulation.  Dependent types are expected to
  bring to multi-stage programming enforcement of strong
  invariants---beyond simple type safety---on the behavior of
  dynamically generated code.  An extension is not trivial, however,
  because a type system would have to take stages---roughly speaking,
  the number of surrounding quotations---of types into account.

  To rigorously study properties of such an extension, we develop
  \LMD, which is an extension of Hanada and Igarashi's typed calculus
  \LTP with dependent types, and prove its properties including
  subject reduction, confluence, strong normalization for full
  reduction, and progress \AI{?} for evaluation semantics.  Motivated
  by code generators such that the type of generated code depends on a
  value from an earlier stage, we argue the significance of
  cross-stage persistence in dependently typed multi-stage programming
  and certain type equivalence that are not directly derived from
  reduction rules.

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\G))                         \\
\end{align*}

>>>>

  We study a dependently typed extension of a multi-stage programming
  language \`a la MetaOCaml, which supports quasi-quotation and
  cross-stage persistence for manipulation of code fragments as
  first-class values and eval for execution of programs dynamically
  generated by the code manipulation.  Dependent types are expected to
  bring to multi-stage programming enforcement of strong
  invariants---beyond simple type safety---on the behavior of
  dynamically generated code.  An extension is, however, not trivial
  because a type system would have to take stages---roughly speaking,
  the number of surrounding quotations---of types into account.

  To rigorously study properties of such an extension, we develop
  \LMD, which is an extension of Hanada and Igarashi's typed calculus
  \LTP with dependent types, and prove its properties including
  preservation, confluence, strong normalization for full
  reduction, and progress for staged reduction.  Motivated
  by code generators such that the type of generated code depends on a
  value from outside of quotations, we argue the significance of
  cross-stage persistence in dependently typed multi-stage programming
  and certain type equivalence that are not directly derived from
  reduction rules.

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\tau))                         \\
\end{align*}
